### 2018-05-23 paper.tex
still need some significant amount of edits

\usepackage{mkolar_definitions}
\usepackage{color}
\usepackage{fullpage}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{array}
\usepackage{natbib}
\usepackage{mathabx}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{multirow}

@@

@@

\begin{abstract}

\end{abstract}

@@

%\newpage

>>>>

\usepackage{mkolar_definitions}

%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{array}
\usepackage{color}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{mathabx}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{wrapfig}

@@

%%%%% Additional Packages

\usepackage{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\RestyleAlgo{boxruled}
\makeatother

\usepackage{apptools}
\usepackage{chngcntr}
\AtAppendix{\counterwithin{lem}{section}}

\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage{titlesec}
\titleformat*{\section}{\normalfont\bfseries}
\titleformat*{\subsection}{\normalfont\bfseries}

%%%%% Additional Definitions

%\DeclareMathOperator*{\argmax}{arg max}
%\DeclareMathOperator*{\argmin}{arg min}
%\DeclareMathOperator*{\diag}{diag}
\DeclareMathOperator*{\diam}{diam}
%\DeclareMathOperator*{\sgn}{sgn}
\DeclareMathOperator*{\supp}{supp}

%\DeclareMathOperator{\Cov}{Cov}
%\DeclareMathOperator{\Var}{Var}

\DeclareMathOperator{\Unif}{Unif}

\def\Db{\mathbf{D}}
\def\Hb{\mathbf{H}}
\def\Ib{\mathbf{I}}
\def\Sbb{\mathbf{S}}
\def\Tb{\mathbf{T}}
\def\Xb{\mathbf{X}}
\def\Yb{\mathbf{Y}}

\def\fate{\boldsymbol{e}}
\def\fath{\boldsymbol{h}}
\def\fatr{\boldsymbol{r}}
\def\fatu{\boldsymbol{u}}
\def\fatv{\boldsymbol{v}}
\def\fatw{\boldsymbol{w}}
\def\fatx{\boldsymbol{x}}
\def\faty{\boldsymbol{y}}
\def\fatz{\boldsymbol{z}}

\def\fatbeta{\boldsymbol{\beta}}
\def\fatgamma{\boldsymbol{\gamma}}
\def\fatdelta{\boldsymbol{\delta}}
\def\fatepsilon{\boldsymbol{\epsilon}}
\def\fateta{\boldsymbol{\eta}}
\def\fatmu{\boldsymbol{\mu}}
\def\fattheta{\boldsymbol{\theta}}
\def\fatpsi{\boldsymbol{\psi}}
\def\fatomega{\boldsymbol{\omega}}

\def\fatDelta{\boldsymbol{\Delta}}
\def\fatLambda{\boldsymbol{\Lambda}}
\def\fatPsi{\boldsymbol{\Psi}}
\def\fatSigma{\boldsymbol{\Sigma}}
\def\fatTheta{\boldsymbol{\Theta}}
\def\fatOmega{\boldsymbol{\Omega}}

\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}

\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}

\newtheorem{lem}{Lemma}[section]
\newtheorem{prop}[lem]{Proposition}

\theoremstyle{definition}
%\newtheorem{assumption}{Assumption}[section]
%\newtheorem{example}{Example}

\theoremstyle{remark}
\newtheorem{rem}{Remark}

\renewcommand{\theassumption}{\arabic{section}.\arabic{assumption}}
\renewcommand{\thethm}{\arabic{section}.\arabic{thm}}
\renewcommand{\thecor}{\arabic{section}.\arabic{cor}}
\renewcommand{\thelem}{\arabic{section}.\arabic{lem}}
\renewcommand{\theprop}{\arabic{section}.\arabic{prop}}

%%%%%

@@

\begin{abstract}
\end{abstract}

@@

\section{Introduction}

Interactions of random variables can be described via \textit{graphical models} whose graphical representation gives us insights into the \emph{structured information} lies in our dataset \cite{Koller2009Probabilistic,Mackay2003}. For example, the interactions among genes can be represented via a graphical model where the presence of edges indicates regulatory activities in gene expressions \cite{Hartemink2000,Dobra2004}.

Undirected graphical models are connected with exponential family distributions via \emph{conditional independence} \cite{Hammersley1971}. If random variable $X_i$ and  $X_j$ are conditionally independent given the rest of random variables, the corresponding parameter $\theta_{i,j}$ in a \emph{pairwise} exponential family model will be zero. If most of the random variable pairs are conditionally independent, our parametrization of the density function will become sparse.

%This observation give rise to the concept of \emph{sparse} graphical model.

Built on a simplicity assumption, a sparse graphical model assumes that there exists only a small number of edges in the graphical structure so the structural sparsity can be in turn translated into the model sparsity. Sparse graphical model, thanks to its interpretability, has become a powerful tool for \emph{high dimensional} data analysis and has been extensively investigated by both practitioners and theoreticians \cite{Friedman2008Sparse,ravikumar09high}.

However, in many applications, interactions among random variables constantly change. For example, genes may regulate each other differently when the external environment is altered. EEG signals from different parts of the brain may be correlated/uncorrelated when the patient performs different activities.
Discovering such changes in graphical models may provide us key insights into the underlying system. A single graphical model, lacking the ability of describing such changes, cannot reflect the dynamic nature of these data.

To obtain \emph{sparse changes} between two graphical models, one can naively learn two sparse graphical models and figure out changes by comparing two separately learned models. However, two issues remain. First, it is unclear how to tune the sparsity level on two individual models in order to obtain the \emph{optimal }differential results. Second, the sparsity assumption imposed on individual graphical models can be too restrictive as sparse changes can be produced by two dense graphical models.

Naturally, one can directly assume the sparsity of the changes themselves without assuming the sparsity level on individual models. This rationale leads to direct sparse changes modelling and learning. Similar to the correspondence between the graphical structure and the graphical model parametrization, the structural change can also be related to the \emph{differential parametrization} between graphical models. In recent years, learning differential parameters of graphical models has become popular in the statistics community. For example, \cite{Zhao2014Direct} proposed to solve a CLIME \cite{Cai2011Constrained}-like optimization problem, while \cite{Liu2016a} and \cite{Fazayeli2016Generalized} estimates the differential parameter via a \emph{density ratio estimation}.

\subsection{Density Ratio Estimation on Learning Graphical Model Changes}
\emph{Density ratio estimation} has been recently introduced to the machine learning community and has been proven useful in a wide range of applications \cite{Sugiyama2012}. It models and learns the ratio between two probability density functions $p$ and $q$ directly rather than work out $p$ and $q$ separately and then take the ratio. The rationale behind this technique is the ``Vapnik's Principle'' : When solving a problem of interest,	one should not solve a more general problem as an intermediate step \cite{Vapnik1998}. The estimated ratio can become a natural ``importance weight'' in transfer learning tasks, such as covariate-shift \cite{Shimodaira2000,Sugiyama2007covariate}. The learned density ratio itself can also quantify the differences between two distributions, thus can be used for change-point detection \cite{Liu2013} and statistical two-sample test \cite{Sugiyama2011}.

Comparing to naive methods that estimate the individual density functions, the density ratio estimation does not directly impose parametric assumptions on the density functions. Instead, it makes assumptions on the ratio, which can be less restraint in some settings. Even for general non-Gaussian graphical models, the estimator has a tractable form that can be constructed from empirical samples in \emph{both} distributions.

Density ratio can be used to characterize the changes between two graphical models. As undirected graphical models can be parametrized as exponential family distributions, the ratio between two exponential family distributions also has an exponential form with the sufficient statistics that is the same as the individual densities and the natural parameter being the \emph{difference} between two natural parameters of individual distributions. Therefore, learning the ratio between two densities can help us identify the changes between two graphical models.

\cite{Liu2014,Liu2016a} studied a specific density ratio estimator called Kullback-leibler Importance Estimation Procedure (KLIEP) \cite{Sugiyama2008} on learning sparse structural changes between graphical models. The $\ell_2$ consistency of KLIEP on Ising models has been proven by generic-chaining technique recently \cite{Fazayeli2016Generalized}.

\subsection{Related Works on Learning Changes between Graphical Models}
Instead of using Density Ratio Estimation, some recent developments on this problem followed a different direction. \cite{Zhao2014Direct} solved a CLIME-like optimization problem making use of a special covariance-precision matrix equality of Gaussian distributions. The optimization is solved directly with respect to the differential parameter itself so  it also does not require extra sparsity assumptions on two individual graphical models. The support consistency of the estimator can be proved. A further investigation shows, the estimator is also consistent on\emph{ transelliptical distributions} \cite{Xu2016Semiparametric}.
In fact, changing graphical models have been studied under  slightly different problem settings. \cite{kolar10estimating} considered a time-varying graphical model that changes \emph{smoothly} over time as well as graphical models with ``jumps''\cite{kolar10estimating}. However, the focuses of these works are not only on the changes, but also on the individual graphical model themselves, thus the direct differential parameter learning method is not useful.

\section{Background}

\subsection{Kullback-Leibler Importance Estimation Procedure (KLIEP) for Change Estimation} \label{subsec:KLIEP}

We start by considering the problem of estimating the difference between a pair of graphs based on an independent pair of samples from each.

Let $\mathcal{F} = \{f(\,\cdot\,;\fateta)\}$ be a parametric family of probability distributions supported on a subset $\mathbb{Y} \subseteq \RR^m$ of the form
\begin{equation}
f(\faty;\fateta)
= Z(\fateta)^{-1} \exp\Big( \sum_{1\leq i\leq j\leq m} \eta_{ij} \, \psi_{ij}(y_i,y_j) \Big)
\quad \text{with} \quad
Z(\fateta) = \int \exp\Big( \sum_{1\leq i\leq j\leq m} \eta_{ij} \, \psi_{ij}(y_i,y_j) \Big) \, d\faty.
\end{equation}
When $\mathcal{Y}$ is discrete, the integral is understood as a sum.
For notational convenience, we shall fix an ordering on the parameter components $\eta_{ij}$, and regard the parameter $\fateta$ as a vector.
Thus, the above is expressed as
\begin{equation}
f(\faty;\fateta)
= Z(\fateta)^{-1} \exp\left( \fateta^\top \fatpsi(\faty) \right)
\quad \text{with} \quad
Z(\fateta) = \int \exp\left( \fateta^\top \fatpsi(\faty) \right) \, d\faty.
\end{equation}
In the graphical model parlance, each $f(\,\cdot\,;\fateta)$ is a Markov random field modeling pairwise dependencies of $m$ nodes.

This class of probability distributions includes many that occur frequently both in theory and in practice.

\begin{example}
$\mathcal{F}$ are Ising models on $m$ nodes if $\faty \in \{-1,+1\}^m$, $\psi(y_i,y_j) = y_iy_j$, and $\eta_{ij} \in \RR$ with $\eta_{ii} = 0$.
\end{example}

\begin{example}
$\mathcal{F}$ are Gaussian graphical models on $m$ nodes if $\faty \in \RR^m$, $\psi(y_i,y_j) = y_iy_j$, and $\fatSigma^{-1} = -\fatLambda$ is positive definite, where $\fatLambda$ is the symmetric matrix with $\Lambda_{ij} = \Lambda_{ji} = \eta_{ij}$ if $i \neq j$, $\Lambda_{ii} = -2 \, \eta_{ii}$ else.
\end{example}

Suppose $f_x = f(\,\cdot\,;\fateta_x)$ and $f_y = f(\,\cdot\,;\fateta_y) \in \mathcal{F}$.
Our goal is to estimate the change
\begin{equation}
\fattheta = \fateta_x - \fateta_y
\end{equation}
based on an independent pair of independent and identically distributed samples
\begin{equation}
\fatx^{(1)}, \dots, \fatx^{(n_x)} \sim f_x
\quad\text{and}\quad
\faty^{(1)}, \dots, \faty^{(n_y)} \sim f_y.
\end{equation}

It may appear that one would have to estimate both $\fateta_x$ and $\fateta_y$ before one could estimate their difference $\fattheta$.
It turns out that this is unnecessary if we adopt the Kullback-Leibler importance estimation procedure (KLIEP), which arises from consideration of the ratio
\begin{equation}
r(\faty;\fattheta)
= \frac{f_x(\faty)}{f_y(\faty)}
= \frac{Z(\fateta_x)^{-1} \exp\left( \fateta_x^\top \fatpsi(\faty) \right)}{Z(\fateta_y)^{-1} \exp\left( \fateta_y^\top \fatpsi(\faty) \right)}
= Z(\fattheta;\fateta_y)^{-1} \exp\left( \fattheta^\top \fatpsi(\faty) \right).
\end{equation}
We shall suppress the dependency on $\fateta_y$ in $Z(\fattheta;\fateta_y)$, and simply write $Z(\fattheta)$.
KLIEP is based on the observation that for each fixed $\fateta_x$ and $\fateta_y$, the true difference $\fattheta^*$ minimizes the Kullback-Leibler divergence from $f_x$ to $r(\,\cdot\,;\fattheta) f_y$, i.e.
\begin{equation}
\begin{aligned}
\fattheta^*
&= \argmin_{\fattheta} \left\{ D_\text{KL}(f_x \,\|\, r(\,\cdot\,;\fattheta) f_y) \right\} \\
&= \argmin_{\fattheta} \left\{ \int \log \left( \frac{f_x(\faty)}{r(\faty;\fattheta) f_y(\faty)} \right) f_x(\faty) \, d\faty \right\}
= -\argmax_{\fattheta} \left\{ \int \log( r(\faty;\fattheta) ) f_x(\faty) \, d\faty \right\}.
\end{aligned}
\end{equation}
Now,
\begin{equation}
\int \log( r(\faty;\fattheta) ) f_x(\faty) \, d\faty
= \int \fattheta^\top \fatpsi(\faty) \, f_x(\faty) \, d\faty - \log Z(\fattheta)
= \EE_x\Big[ \fattheta^\top \fatpsi(\fatx) \Big] - \log \EE_y\Big[ \exp\left( \fattheta^\top \fatpsi(\faty) \right) \Big],
\end{equation}
where the equivalence of the second terms in the last equality is because
\begin{equation}
\int r(\faty;\fattheta) f_y(\faty) \, d\faty
= \int \frac{f_x(\faty)}{f_y(\faty)} f_y(\faty) \, d\faty
= \int f_y(\faty) \, d\faty
= 1,
\end{equation}
and so
\begin{equation}
\EE_y\left[ \exp\left( \fattheta^\top \fatpsi(\faty) \right) \right]
= \int \exp\left( \fattheta^\top \fatpsi(\faty) \right) f_y(\faty) \, d\faty
= Z(\fattheta) \int r(\faty;\fattheta) f_y(\faty) \, d\faty
= Z(\fattheta).
\end{equation}
Thus,
\begin{equation} \label{eq:EKLIEP}
\fattheta^*
= \argmin_{\fattheta} \Big\{ -\EE_x\Big[ \fattheta^\top \fatpsi(\fatx) \Big] + \log \EE_y\Big[ \exp\left( \fattheta^\top \fatpsi(\faty) \right) \Big] \Big\}.
\end{equation}

In practice, the expectations in (\ref{eq:EKLIEP}) are approximated by their empirical versions to form the empirical KLIEP loss
\begin{equation}
\begin{aligned}
\ell_\text{KLIEP}(\fattheta;\Xcal,\Ycal)
&:= -\hat\EE_x\Big[ \fattheta^\top \fatpsi(\fatx^{(i)}) \Big] + \log \hat\EE_y\Big[ \exp\left( \fattheta^\top \fatpsi(\faty^{(j)}) \right) \Big] \\
&= -\frac{1}{n_x} \sum_{i=1}^{n_x} \fattheta^\top \fatpsi(\fatx^{(i)}) + \log\left[ \frac{1}{n_y} \sum_{j=1}^{n_y} \exp\left( \fattheta^\top \fatpsi(\faty^{(j)}) \right) \right].
\end{aligned}
\end{equation}
Denote the sample estimate of $Z(\fattheta)$ by
\begin{equation}
\hat Z(\fattheta)
= \hat Z(\fattheta;\Ycal)
:= \hat\EE_y\left[ \exp\left( \fattheta^\top \fatpsi(\faty^{(j)}) \right) \right]
= \frac{1}{n_y} \sum_{j=1}^{n_y} \exp\left( \fattheta^\top \fatpsi(\faty^{(j)}) \right)
\end{equation}
and define
\begin{equation}
\hat r(\faty;\fattheta)
= \hat r(\faty;\fattheta,\Ycal)
:= \hat Z(\fattheta)^{-1} \exp\left( \fattheta^\top \fatpsi(\faty) \right),
\end{equation}
the plug-in estimate of the ratio $r(\faty;\fattheta)$.
Direct computations yield
\begin{equation}
\nabla \ell_\text{KLIEP}(\fattheta;\Xcal,\Ycal)
= -\frac{1}{n_x} \sum_{i=1}^{n_x} \fatpsi(\fatx^{(i)}) + \frac{1}{n_y} \sum_{j=1}^{n_y} \fatpsi(\faty^{(j)}) \hat r(\faty^{(j)};\fattheta)
\end{equation}
and
\begin{equation}
\begin{aligned}
\nabla^2 \ell_\text{KLIEP}(\fattheta;\Ycal)
&= \fatPsi(\Ycal) \left[ \frac{1}{n_y} \diag(\hat\fatr(\Ycal;\fattheta)) - \frac{1}{n_y^2} \hat\fatr(\Ycal;\fattheta)\hat\fatr(\Ycal;\fattheta)^\top \right] \fatPsi(\Ycal)^\top \\
&= \frac{1}{n_y^2} \sum_{1 \leq j < j' \leq n_y} \left( \fatpsi(\faty^{(j)}) - \fatpsi(\faty^{(j')}) \right) \left( \fatpsi(\faty^{(j)}) - \fatpsi(\faty^{(j')}) \right)^\top \hat r(\faty^{(j)};\fattheta) \hat r(\faty^{(j')};\fattheta)
\end{aligned}
\end{equation}
where $\fatPsi(\Ycal)$ is the $p$-by-$n_y$-matrix whose $j$-th column is $\fatpsi(\faty^{(j)})$, the vector of sufficient statistics for the $j$-th $\faty$-sample, and $\hat \fatr(\Ycal;\fattheta)$ is the $n_y$-vector whose $j$-th component is $\hat r(\faty^{(j)};\fattheta)$, the $j$-th ratio estimate.

We note that the Hessian depends on the data only through the $\faty$-samples.
Moreover, it is clear from the form of the Hessian that $\ell_\text{KLIEP}$ is convex as a function of $\fattheta$, and that it is {\it never} strongly convex for $n_y \leq p$.
Specifically, the Hessian is positive semi-definite with rank at most $n_y - 1$.
This is why it is more desirable to choose $\faty$ as the larger of the two samples.
This is especially the case when the estimates have to be de-biased, as we shall soon see.

When $n_y$ is sufficiently large, we estimate $\fattheta$ as the minimizer of $\ell_\text{KLIEP}$
\begin{equation}
\hat\fattheta = \argmin_{\fattheta} \left\{ \ell_\text{KLIEP}(\fattheta;\Xcal,\Ycal) \right\}.
\end{equation}
When $n_y \leq p$
\begin{equation}
\hat\fattheta_\lambda = \argmin_{\fattheta} \left\{ \ell_\text{KLIEP}(\fattheta;X,Y) + \lambda\|\fattheta\|_1 \right\}
\quad \text{for some} \quad \lambda > 0
\end{equation}
has been shown to be consistent subject to conditions.

\subsection{De-Biasing Procedures for High-Dimensional Estimators}

We derive de-biasing procedures for constructing an asymptotically normal estimator of a scalar component of interest in the presence of a high-dimensional nuisance component using the outcome of penalized estimation procedures.
For notational convenience, let $\ell(\fattheta) = \ell_\text{KLIEP}(\fattheta)$, and $\fattheta = (\theta_1,\fattheta_2)$, where $\theta_1 \in \RR$ is considered the target and $\fattheta_2 \in \RR^{p-1}$, the nuisance.
We denote the true value of the parameter as $\fattheta^*$.
Although our exposition occurs in the context of KLIEP, $\ell$ can be any convex loss with first derivatives decomposing into a sum of independent terms and second derivatives satisfying certain regularity conditions, e.g.~$\ell \in \mathscr{C}^2(\RR^p \to \RR)$.

Suppose we would like to make a valid statistical statement about $\theta_1$.
Examples include conducting hypothesis tests or constructing confidence intervals at level $\alpha \in (0,1)$.

In the unlikely scenario in which we have access to the true nuisance parameter $\fattheta_2^*$, we can plug $\fattheta_2^*$ into $\ell$ to obtain $\ell(\,\cdot\,,\fattheta_2)$, which is now a function defined on the real line.
Knowing $\fattheta_2^*$ effectively reduces the dimension of the estimation problem to one, and there is no need to distinguish between a high-dimensional setting and a low-dimensional one.

Of course, it is highly unlikely that $\fattheta_2^*$ is ever known to us, but we usually have ways of estimating it consistently.
By analogy to the infeasible case, given an estimator $\check\fattheta_2$, the intuitive thing to do may be to plug it into $\ell$ and solve the resulting one-dimensional problem.
However, the particular setting does turn out to matter in this case, and the intuitive solution may or may not be correct.

To see why, consider the Taylor expansion of $\ell$ about $\fattheta^*$:
\begin{equation} \label{eq:Taylor_line1}
\partial_1 \ell(\theta_1,\fattheta_2)
= \partial_1 \ell(\theta_1^*,\fattheta_2^*) + \bar\Hb_{11} (\theta_1 - \theta_1^*) + \bar\Hb_{12} (\fattheta_2 - \fattheta_2^*),
\end{equation}
where $\bar\Hb_{11}$ and $\bar\Hb_{12}$ are sub-matrices of the matrix
\begin{equation} \label{eq:rem}
\bar\Hb
= \bar\Hb(\fattheta)
= \begin{bmatrix} \bar\Hb_{11}(\fattheta) & \bar\Hb_{12}(\fattheta) \\ \bar\Hb_{21}(\fattheta) & \bar\Hb_{22}(\fattheta) \end{bmatrix}
= \int_0^1 \nabla^2 \ell\big( \fattheta^* + t (\fattheta-\fattheta^*) \big) \, dt.
\end{equation}
Suppose we were to adapt the plug-in approach to obtain $\check\fattheta = (\check\theta_1,\check\fattheta_2)$.
The corresponding Taylor expansion is got by setting $\theta_1 = \check\theta_1$, $\fattheta_2 = \check\fattheta_2$.
In this case, the left-hand side of (\ref{eq:Taylor_line1}) is identically zero by definition of $\check\theta_1$, and the first term on the right-hand side converges to a centered normal distribution for most loss functions that are seen in practice.
Since $\bar\Hb_{11}$ can be shown to be invertible with high probability if the population covariance is invertible, $\check\theta_1$ will converge to a normal distribution provided that $\check\fattheta_2$ is itself asymptotically normal and unbiased.

When $n \gg p$, it is easy to obtain an estimator of the nuisance parameter that is already asymptotically normal and unbiased.
Indeed, minimizing the full loss and accounting for the variance in the nuisance part of the estimated parameter vector yields a valid inference for $\theta_1$.
Things are more delicate when $n_y \ll p$, as it is usually impossible to estimate high-dimensional parameters consistently without introducing some bias.
Moreover, most high-dimensional procedures imply some form of variable selection, and the limiting distribution of the resulting estimators are intractable in general.
Thus, the plug-in approach yields a valid procedure in the classical setting, but this validity fails to carry over into the high-dimensional regimes.

De-biasing techniques attempts to remedy this issue in high-dimensions, at least for cases when some structural assumptions are satisfied.
The key idea that is common to these methods is to temper the effect of a perturbation in the nuisance component by re-expressing $\fattheta_2 - \fattheta_2^*$ in terms of the higher-order terms of the Taylor expansion.
This is related to Neyman's construction of the $C(\alpha)$ test.

To explore this idea in more detail, we look at the full Taylor expansion with respect to not only the parameter of interest but also the nuisance component.
\begin{align}
\label{eq:Taylor1}
\partial_1 \ell(\theta_1,\fattheta_2)
&= \partial_1 \ell(\theta_1^*,\fattheta_2^*) + \bar\Hb_{11} (\theta_1 - \theta_1^*) + \bar\Hb_{12} (\fattheta_2 - \fattheta_2^*), \\
\label{eq:Taylor2}
\partial_2 \ell(\theta_1,\fattheta_2)
&= \partial_2 \ell(\theta_1^*,\fattheta_2^*) + \bar\Hb_{21} (\theta_1 - \theta_1^*) + \bar\Hb_{22} (\fattheta_2 - \fattheta_2^*).
\end{align}
When $\fattheta = (\theta_1,\fattheta_2)$ is sufficiently close to $\fattheta^* = (\theta_1^*,\fattheta_2^*)$, we expect $\bar\Hb$ to be close to $\Hb^* = \nabla^2 \ell(\fattheta^*)$, and hence, to $\Ib^* = \EE\Hb^* = \EE\nabla^2 \ell(\fattheta^*)$.
Thus, it is helpful to re-write (\ref{eq:Taylor1}) and (\ref{eq:Taylor2}) as
\begin{align}
\label{eq:proxy_Taylor1}
\partial_1 \ell(\theta_1,\fattheta_2)
&= \partial_1 \ell(\theta_1^*,\fattheta_2^*) + \Ib^*_{11} (\theta_1 - \theta_1^*) + \Ib^*_{12} (\fattheta_2 - \fattheta_2^*) + \Delta_1, \\
\label{eq:proxy_Taylor2}
\partial_2 \ell(\theta_1,\fattheta_2)
&= \partial_2 \ell(\theta_1^*,\fattheta_2^*) + \Ib^*_{21} (\theta_1 - \theta_1^*) + \Ib^*_{22} (\fattheta_2 - \fattheta_2^*) + \fatDelta_2,
\end{align}
where
\begin{equation}
\fatDelta
= \begin{bmatrix} \Delta_1 \\ \fatDelta_2 \end{bmatrix}
= \begin{bmatrix} [ \bar\Hb_{11} - \Ib^*_{11} ] (\theta_1 - \theta_1^*) + [ \bar\Hb_{12} - \Ib^*_{12} ] (\fattheta_2 - \fattheta_2^*) \\ [ \bar\Hb_{21} - \Ib^*_{21} ] (\theta_1 - \theta_1^*) + [ \bar\Hb_{22} - \Ib^*_{22} ] (\fattheta_2 - \fattheta_2^*) \end{bmatrix}
= [ \bar\Hb - \Ib^* ] (\fattheta - \fattheta^*)
\end{equation}
is expected to be small.

Suppose $\Ib^*$ is invertible.
In most concrete problems, this would amount to assuming that a population covariance is strictly positive definite.
By the Schur complement condition, both $\Ib^*_{22}$ and its Schur complement $\Ib^*_{11} - \Ib^*_{12} \Ib^{*-1}_{22} \Ib^*_{21}$ are positive definite, so (\ref{eq:proxy_Taylor2}) can be solved for $\fattheta_2 - \fattheta_2^*$ as
\begin{equation} \label{eq:approx_diff_nui}
\fattheta_2 - \fattheta_2^*
= \Ib^{*-1}_{22} \left( \partial_2 \ell(\theta_1,\fattheta_2) - \partial_2 \ell(\theta_1^*,\fattheta_2^*) - \Ib^*_{21} (\theta_1 - \theta_1^*) - \fatDelta_2 \right).
\end{equation}
Substituting (\ref{eq:approx_diff_nui}) into (\ref{eq:proxy_Taylor1}),
\begin{multline}
\partial_1 \ell(\theta_1,\fattheta_2) - \Ib^*_{12} \Ib^{*-1}_{22} \partial_2 \ell(\theta_1,\fattheta_2) \\
= \partial_1 \ell(\theta_1^*,\fattheta_2^*) - \Ib^*_{12} \Ib^{*-1}_{22} \partial_2 \ell(\theta_1^*,\fattheta_2^*) + (\Ib^*_{11} - \Ib^*_{12} \Ib^{*-1}_{22} \Ib^*_{21}) (\theta_1 - \theta_1^*)  + \Delta_1 - \Ib^*_{12} \Ib^{*-1}_{22} \fatDelta_2,
\end{multline}
or, equivalently,
\begin{multline} \label{eq:Taylor_orth_score}
\left\langle \begin{bmatrix} 1 \\ -\Ib^*_{12} \Ib^{*-1}_{22} \end{bmatrix},
\begin{bmatrix} \partial_1 \ell(\theta_1,\fattheta_2) \\ \partial_2 \ell(\theta_1,\fattheta_2) \end{bmatrix} \right\rangle \\
=
\left\langle \begin{bmatrix} 1 \\ -\Ib^*_{12} \Ib^{*-1}_{22} \end{bmatrix},
\begin{bmatrix} \partial_1 \ell(\theta_1^*,\fattheta_2^*) \\ \partial_2 \ell(\theta_1^*,\fattheta_2^*) \end{bmatrix} \right\rangle
+ (\Ib^*_{11} - \Ib^*_{12} \Ib^{*-1}_{22} \Ib^*_{21}) (\theta_1 - \theta_1^*)
+ \left\langle \begin{bmatrix} 1 \\ -\Ib^*_{12} \Ib^{*-1}_{22} \end{bmatrix},
\begin{bmatrix} \Delta_1 \\ \fatDelta_2 \end{bmatrix} \right\rangle.
\end{multline}

Thus, by leveraging (\ref{eq:proxy_Taylor2}) to find an expression for $\fattheta_2 - \fattheta_2^*$ in terms of the linear and quadratic terms of the nuisance Taylor expansion, we have succeeded in removing the lower-order effects of perturbation in $\fattheta_2$ from the Taylor expansion for $\theta_1$.

Now, the block matrix inversion formula says the row of the inverse of $\Ib^*$ corresponding to the parameter of interest is precisely
\begin{equation}
\fatomega^{*\top}
:= (\Ib^*_{11} - \Ib^*_{12} \Ib^{*-1}_{22} \Ib^*_{21})^{-1} \begin{bmatrix} 1 & -\Ib^*_{12} \Ib^{*-1}_{22} \end{bmatrix},
\end{equation}
the vector that defines the modified score up to the scalar $(\Ib^*_{11} - \Ib^*_{12} \Ib^{*-1}_{22} \Ib^*_{21})^{-1}$.
Thus, (\ref{eq:Taylor_orth_score}) is equivalent to
\begin{equation} \label{eq:infeasible_Bahadur}
\sqrt{n} \, (\theta_1 - \theta_1^*)
-\sqrt{n} \, \langle \fatomega^*, \nabla \ell(\theta_1,\fattheta_2) \rangle
=
-\sqrt{n} \, \langle \fatomega^*, \nabla \ell(\theta_1^*,\fattheta_2^*) \rangle
-\sqrt{n} \, \langle \bar\Hb \fatomega^* - \fate_1, \fattheta - \fattheta^* \rangle.
\end{equation}

Ignoring the issue of not knowing $\fatomega^*$ for the moment, (\ref{eq:infeasible_Bahadur}) is nearly the expansion we want.
If $\hat\fattheta = (\hat\theta_1,\hat\fattheta_2)$ can be chosen as a solution to
\begin{equation}
\langle \fatomega^*, \nabla \ell(\theta_1,\fattheta_2) \rangle = 0,
\end{equation}
then provided that the last term is negligible in the limit, $\theta_1$ must be asymptotically normal and unbiased, because the first term on the right-hand side usually converges to a centered normal distribution by some form of the central limit theorem.

As $\fatomega^*$ is also a population-level quantity, it must be estimated from the data.
We study the effect of the perturbation in $\fatomega$ on (\ref{eq:infeasible_Bahadur}).
\begin{multline} \label{eq:feasible_Bahadur}
\sqrt{n} \, (\theta_1 - \theta_1^*)
-\sqrt{n} \, \langle \fatomega, \nabla \ell(\theta_1,\fattheta_2) \rangle \\
=
-\sqrt{n} \, \langle \fatomega^*, \nabla \ell(\theta_1^*,\fattheta_2^*) \rangle
-\sqrt{n} \, \langle \fatomega - \fatomega^*, \nabla \ell(\theta_1,\fattheta_2) \rangle
-\sqrt{n} \, \langle \bar\Hb \fatomega^* - \fate_1, \fattheta - \fattheta^* \rangle.
\end{multline}

Given a ``good" estimator $\hat\fatomega$ of $\fatomega^*$, we have two ways of obtaining $\hat\theta_1$.
The first procedure, double selection, first estimates the support of $\fattheta^*$ and $\fatomega^*$ via $\check\fattheta$ and $\check\fatomega$, and then re-estimates both parameters restricting to the union of the estimated supports $\supp(\check\fattheta) \cup \supp(\check\fatomega)$.
The resulting pair automatically satisfies
\begin{equation}
\langle \hat\fatomega, \nabla \ell(\hat\theta_1^\text{ds},\hat\fattheta_2) \rangle = 0
\end{equation}
by the first-order conditions of the re-fitting problem.
The implied linear representation is
\begin{multline}
\sqrt{n} \, (\hat\theta_1^\text{ds} - \theta_1^*) \\
=
-\sqrt{n} \, \langle \fatomega^*, \nabla \ell(\theta_1^*,\fattheta_2^*) \rangle
-\sqrt{n} \, \langle \hat\fatomega - \fatomega^*, \nabla \ell(\hat\theta_1,\hat\fattheta_2) \rangle
-\sqrt{n} \, \langle \bar\Hb \fatomega^* - \fate_1, \hat\fattheta - \fattheta^* \rangle.
\end{multline}

The second, one-step, obtains $\check\fattheta$ and $\check\fatomega$ via penalized estimation procedures, and computes
\begin{equation}
\hat\theta_1^\text{1step} = \check\theta_1 - \langle \check\fatomega, \nabla \ell(\check\theta_1,\check\fattheta_2) \rangle.
\end{equation}
Then, $\sqrt{n} \, (\hat\theta_1^\text{1step} - \theta_1^*)$ is exactly the left-hand side of the expansion in (\ref{eq:feasible_Bahadur}) so that the implied linear representation is
\begin{multline}
\sqrt{n} \, (\hat\theta_1^\text{1step} - \theta_1^*) \\
=
-\sqrt{n} \, \langle \fatomega^*, \nabla \ell(\theta_1^*,\fattheta_2^*) \rangle
-\sqrt{n} \, \langle \check\fatomega - \fatomega^*, \nabla \ell(\check\theta_1,\check\fattheta_2) \rangle
-\sqrt{n} \, \langle \bar\Hb \fatomega^* - \fate_1, \check\fattheta - \fattheta^* \rangle.
\end{multline}
